Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

    \item {{\bf Type 2:}} $h$ or $v$ fails to cross some rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. This means the existence of at least one rectangle $r_i$, for some $i \in [k-2]$, covers either an endpoint of $h$, or an endpoint of $v$, or both.
}
Figure~\ref{fig:hv:cats} illustrates a result tuple of each type, assuming $k = 4$.

\begin{figure} 
    \begin{tabular}{cc} 
        \includegraphics[height=27mm]{./artwork/cat1} & 
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/cat2} \\
        (a) Cat.\ 1 result tuple & 
        (b) Cat.\ 2 result tuple
    \end{tabular}

@@

>>>>

    \item {{\bf Type 2:}} $h$ or $v$ fails to cross some rectangle in $\set{r_1, r_2, ..., r_{k-2}}$. This means the existence of at least one rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of either $h$ or $v$ or both.
}
Figure~\ref{fig:hv:types} illustrates a result tuple of each type, assuming $k = 4$.

\begin{figure} 
    \begin{tabular}{cc} 
        \includegraphics[height=27mm]{./artwork/type1} & 
        \hspace{5mm} \includegraphics[height=27mm]{./artwork/type2} \\
        (a) Cat.\ 1 result tuple & 
        (b) Cat.\ 2 result tuple
    \end{tabular}

@@

We will find result tuples of each type separately. Before proceeding, however, let us observe a sense of symmetry for Type 2. As mentioned, for a result tuple $(r_1, ..., r_{k-2}, h, v)$ of this type, a rectangle $r_i$, for some $i \in [k-2]$, covers an endpoint of $h$ or $v$ or both. As (i) there are $k-2$ choices for $i$ and (ii) $h$ and $v$ together have four endpoints, we can divide Type 2 further into $4(k-2)$ ``sub-types'': e.g., in subtype 1 (resp., 2), $r_1$ covers the left (resp., right) endpoint of $h$, in subtype 3 (resp., 4), $r_1$ covers the bottom (resp., top) endpoint of $v$, etc. It is possible for the result tuple to belong to multiple sub-types simultaneously.

Our subsequent discussion will proceed as follows. In Section~\ref{sec:hv:type1}, we

\subsection{Finding Result Tuples of Type 1} \label{sec:hv:type1}

\subsection{Finding Result Tuples of Type 2} \label{sec:hv:type2}
